Experiment 3: ratings

### 2021-06-07 analysis/exp3_analysis.Rmd
directly compare model vs. likelihood ratings

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

@@

p2 <- adult_agg %>% left_join(trials %>% select(drop, target, distractor, relation, prop_target_supp)) %>%
  ggplot(aes(x=prop_target_supp, y=prop_targ_lik, color=relation)) + geom_point(alpha=.8) +
  xlab("Prop. Target Support SD in Model") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson") 
  stat_cor(inherit.aes = F, aes(x=prop_target_supp, y=prop_targ_lik, 
               label = paste(..rr.label.., sep = "~`,`~")))

@@

>>>>

## Load packages

@@

p2 <- adult_agg %>% left_join(trials %>% select(drop, target, distractor, relation, prop_target_supp)) %>%
  ggplot(aes(x=prop_target_supp, y=prop_targ_lik, color=relation)) + geom_point(alpha=.8) +
  xlab("Prop. Target Support SD in Model") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(inherit.aes = F, aes(x=prop_target_supp, y=prop_targ_lik, 
               label = paste(..rr.label.., sep = "~`,`~")))

@@

## Directly compare ratings to model probs

```{r}
mdat <- mdat %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice"))

p1 <-mdat %>% ggplot(aes(x=likelihood, y=support_probability, color=relation)) +
  geom_point(alpha=.7) + theme_classic() + xlab("Adults' Mean Likelihood Rating") +
  stat_cor(inherit.aes = F, aes(x=likelihood, y=support_probability, 
               label = paste(..rr.label.., sep = "~`,`~")))

p2 <- mdat %>% ggplot(aes(x=likelihood, y=support_std, color=relation)) +
  geom_point(alpha=.7) + theme_classic() + xlab("Adults' Mean Likelihood Rating") +
  stat_cor(inherit.aes = F, aes(x=likelihood, y=support_std, 
               label = paste(..rr.label.., sep = "~`,`~")))

Other feature correlations

```{r}
with(mdat, cor(likelihood, support_probability)) # r=.75
with(mdat, cor(likelihood, support_std)) # .77
with(mdat, cor(likelihood, support_sharpness_accuracy_mean)) # .496
with(mdat, cor(likelihood, support_response_linearity_r)) # .48
with(mdat, cor(likelihood, support_response_linearity_pv)) # .53
```
